---
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
output: pdf_document
bibliography: references.bib 
nocite: '@*'
header-includes:
- \usepackage{setspace}
- \onehalfspacing
---

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, highlight=FALSE, message=FALSE, fig.align = "center")
```

```{r, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE}
# Library statements
library(knitr)
```

# Data
The dataset we intend to use for this project pertains to three of our past social media marketing campaigns, and contains 1,143 observations across eleven variables. Of these eleven variables, two have been selected and removed for reasons which will be discussed further below. Each row of data can be thought of as a unique advertisement tied to one of three online marketing campaigns, and is further composed of demographic data on the audience to which the ad was shown, and various advertisement performance metrics. Facebook defines an audience as a group of users that matches a set of demographic characteristics specified by the advertising firm (Facebook n.d.).
\newline

The first two columns of data within our dataset contain identifiers associated with each individual advertisement and the specific past marketing campaign each advertisement was part of. One column of  demographic information corresponds to the average value of the age bracket associated with a particular audience. For ease of future analyses, audiences in their early thirties are assigned the value 32, while audiences in their late thirties are assigned the value 37, and so on.  The other column of demographic information contains binary values corresponding to the gender makeup of a particular audience, with a 1 representing a male audience and a 0 representing a female audience. The dataset does not appear to account for non-binary gender identities, perhaps due to its age.
\newline

The following are descriptions of the advertisement performance measures included in the dataset. One such column contains information on the number of times a particular advertisement was shown to a particular audience, whereas another contains information on the number of times a particular audience clicked on a particular advertisement. A subsequent column of data pertains to the dollar amount our firm paid Facebook in order to have a particular advertisement delivered to a particular audience. The last two columns correspond to the number of total and approved conversions ultimately generated by each advertisement deployed by our firm. 

## Data collection
This dataset was obtained through one of our firm’s data exports onto an online data repository (Gokagglers 2017). The combination of qualitative and quantitative information contained within the dataset should be quite suitable for the analytical processes our team plans to carry out. The subsequent analysis should lead to the discovery of valuable insights into effective advertising and marketing strategies. Furthermore, the dataset appears to be of high quality, containing data that is clean and easy to interpret while also being free of any missing information. The expectation is that the data should allow us to infer which key performance indicators most strongly contribute to the performance of a marketing campaign.

## Data preparation
Our team tackled the task of preparing the dataset by first checking whether it contained any missing information that we would need to address. This is important because the presence of missing data can pose a number of serious problems for our data analysis going forward (Kang 2013). Fortunately, we were able to confirm that our dataset was complete and free of any missing data. We then proceeded to convert the data within the columns into formats that would be easier to manipulate and interpret through the use of statistical software. In the case of target audience age, audiences in their early thirties (30-34) are assigned the value 32, while audiences in their late thirties (35-39) are assigned the value 37, and so on. Target audience gender was also converted into a binary number format with a value of 1 for male and 0 for female.
\newline

Next, we removed two columns containing redundant and meaningless data that were not useful to us. A column containing Facebook’s advertisement identification numbers was removed because the first column in our dataset already provides a unique per-advertisement identification number. A column containing numeric codes which Facebook assigns to its users based on information available on their public profiles was removed because the codes were impossible to interpret in the context of our dataset. Without any information on the products being advertised in the anonymized marketing campaigns and the interest groups associated with these codes, the values proved essentially meaningless. We encountered no further considerations regarding our data.