---
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
output: pdf_document
bibliography: references.bib 
nocite: '@*'
header-includes:
- \usepackage{setspace}
- \onehalfspacing
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, highlight=FALSE, message=FALSE)
```

```{r}
# Library statements
```

# Introduction
A continuing pattern of rapid technological development and the widespread adoption of digital services over the past decade has led to a meteoric rise and expansion of electronic commerce and online business. These disruptions continue to shake the foundations underlying traditional brick-and-mortar stores which have historically been unmoving cornerstones of the retail industry. The ongoing COVID-19 pandemic has only made these transformations more glaringly apparent. Retail giants such as Best Buy and Nordstrom have managed to retain over 60-70% of their sales volume during the past year by leveraging their online sales platforms (Walton 2020). Our firm has sensibly positioned itself thus far to stay ahead of these shifting commercial tides through the early adoption of digital marketing practices. However, we still stand to gain much as an organization by leveraging business analytics to illuminate new opportunities and avenues for growth.

## Business problem
The objective of this analytical project will be to explore data collected from our organization’s past Facebook marketing campaigns to identify the factors that most contributed to our past success, as well as areas of improvement for future growth. Identifying the key performance indicators and demographic characteristics that are most consistently associated with higher sales conversion should be instrumental in the development of data driven strategies that will guide our future marketing efforts.
\newline

Furthermore, ensuring that we are targeting the appropriate demographics should allow us to build and maintain stronger customer relationships. The importance of preserving customer loyalty has only risen alongside the proliferation of digital marketing channels, as the process of browsing through store to store has quickly been reduced to a simple matter of a few clicks (RetailNext 2014). We will need to be aware of the challenge this poses as we work towards expanded sales and sustained growth.

## Intended audience
The details covered in this project are likely to be of interest to firms across diverse sectors. Consumers of all kinds have long made evident their demand for e-commerce. The COVID-19 pandemic has only further accelerated the need for online marketing practices as social distancing measures, business shutdowns, and stay-at-home orders have led to an increase in contactless shopping and on-demand fulfillment. By mid-April 2020 alone, online orders grew 68%, surpassing 40% of total retail sales, with meaningful gains in categories where digital commerce penetration had been historically low, such as grocery products (Deloitte 2020).
\newline

Of course, the results from our analysis will still be specifically tailored to our firm’s marketing strategies. As such, it will be difficult for other firms to simply take our findings at face value and apply them with any real degree of success. After all, firms are differentiated by numerous characteristics and typically compete on varying market segments. The analytical procedures we carry out, on the other hand, can probably be tuned, adjusted, and adapted for external use.