---
title: \vspace{2.25in} Boosting Brand Recognition and Sales by Exploring Facebook Advertising Data
author: 
- "Prepared by:"
- Andrew Cho
- Byoung Chul Hwang
- Abhi Opesh
- Chethan Shivaram
date: May 6, 2021
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
output: 
  pdf_document:
    toc_depth: 3
    number_sections: true
bibliography: references.bib
nocite: '@*'
header-includes:
- \usepackage{setspace}
- \onehalfspacing
- \renewcommand{\and}{\\}
- \usepackage[nottoc]{tocbibind}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, highlight=FALSE, message=FALSE)
```

\pagenumbering{gobble}

\newpage 
\pagenumbering{roman} 

\tableofcontents 


\newpage

\renewcommand{\listtablename}{List of tables}
\listoftables

\renewcommand{\listfigurename}{List of figures}
\listoffigures


\newpage
\pagenumbering{arabic} 

# Executive summary {-}
This report provides a comprehensive analysis of data from three of our past social media marketing campaigns with the intent of identifying the factors which most strongly contributed to our past marketing success, as well as opportunities for future growth. Data is cleaned, prepared and explored before being used to train and build a suite of statistical predictive models. The exploratory findings indicate that our investment in online marketing activities has ramped up over time, suggesting that the firm is keeping up with a growing trend of digital service adoption. Additionally, landing page conversion rates are found to be commensurate with industry standards, indicating steady performance.
\newline

The regression analysis results indicate that the number of impressions generated over the course of an advertisement’s deployment is the most significant predictor of greater sales conversion. In terms of demographic characteristics, the results indicate that target audience age is the most significant predictor of greater sales conversion. On the other hand, target audience gender is shown to be of relatively low importance in this regard.
\newline

Recommendations are discussed in more detail towards the end of the report. They include: focusing strategic efforts on targeting the right age groups, discounting the importance of targeting specific gender groups, conducting further analyses of CPC and CPM pricing options, and conducting further research into the defining characteristics of Campaign 2.

\newpage
```{r, child='Deliverable1 final.Rmd'}
## IMPORTANT!!
## REMOVE the required data section.
## REMOVE the \newpage and # References from the end.
```

```{r, child='Deliverable2 final.Rmd'}
## IMPORTANT!!
## MOVE the data preparation details section to appendix B.
## REMOVE the \newpage and # References from the end.
```

```{r, child='Deliverable3 final.Rmd'}
## IMPORTANT!!
## MOVE the descriptive analytics details section to appendix C.
## REMOVE THE \newpage and # References from the end.
```
 
```{r, child='Deliverable4 final.Rmd'}
## IMPORTANT!!
## MOVE the predictive analytics details section to appendix C.
## REMOVE THE \newpage and # References from the end.
```

# Conclusions
Our analysis indicates that there are a few KPIs that are strongly associated with higher sales conversion. Based on our predictive analytics, a marketing campaign’s success as measured by total and approved conversion is largely dependent on the number of times an ad was shown to target audiences. In addition to the number of impressions an advertisement manages to generate, the social media marketing performance also appears to depend heavily on the amount of per-advertisement spending.
\newline
 
Initial descriptive analytics showed the strongest relationships between per-advertisement spending and impressions, as well as between clicks and impressions. Our data exploration also indicated that there were no advertisements with zero clicks and nonzero spending, which is consistent with the CPC pricing model our firm employs on the Facebook platform. Interestingly, we noted that the relationship between the number of audience clicks and the number of resultant conversions was one of the weakest among the different variables in our dataset. This initial finding appears to be incongruent with the results of our predictive analysis, which indicate that the number of audience clicks has a significant effect on the number of realized conversions. 
\newline
 
Our models indicate that target audience age is a significant predictor of total conversion. As per our descriptive analysis, we note that the most frequently occurring age demographic among our target audiences consists of males aged 30 to 34, followed by females aged 30 to 34. The three remaining age ranges consist of older individuals and trails slightly behind in terms of frequency of occurrence. These findings seem to indicate that younger audiences tend to inquire about our products more frequently than those that are older. We do not observe the same effect when it comes to actually converting these website inquiries into sales, however. It is quite possible that this has little do do with the efficacy of our Facebook marketing strategy and more to do with the design of our online sales platform itself. Additionally, we that target audience gender does not have a significant effect on conversion.
\newline
 
Finally, an exploration of the characteristics of the three marketing campaigns described in the dataset indicate substantial differences between the three. Campaign 3 demonstrates the greatest variability and median measurements across most of the aforementioned metrics in our data. It is worth noting that Campaign 3 consisted of 625 advertisements, while Campaign 2 consisted of 464 and Campaign 1 consisted of only 54. Accordingly, Campaign 3 also appeared to have enjoyed the highest level of engagement among target audiences. This disparity in observation counts appears to have been borne out in our models as well. Information regarding an advertisement’s association with Campaign 1 was insignificant while the same for Campaign 2 was highly significant.

# Recommendations

1. **Focus strategic efforts on targeting the right age groups**
\newline

Our results indicate that target audience age is the single most important demographic characteristic with respect to maximizing sales conversion. Findings also show that younger audiences tended to inquire about the product more often. Further market research into audiences aged 20-24 and 25-29 could prove especially valuable.
\newline

2. **Discount importance of targeting specific gender groups**
\newline

The findings point to target audience gender being one of the least important factors with respect to maximizing sales conversion. This suggests that demand for our product is similar across different gender groups, and that it may not be worth expending limited resources to identify and target specific gender groups.
\newline

3. **Conduct further analyses of CPC and CPM pricing models**
\newline

Our models show that the number of impressions generated by an advertisement is a stronger predictor of sales conversion than the number of audience clicks. However, it would be difficult to make a case for a switch from a CPC to a CPM pricing model without a deeper understanding of the marginal costs and benefits of either option. It is entirely possible that such a transition could lead to higher advertising costs without any significant performance improvements.
\newline

4. **Conduct further research into the defining characteristics of Campaign 2**
\newline

Our models suggest that an advertisement's association with Campaign 2 may have implications for both total and approved conversion. More research should be done into the defining characteristics of Campaign 2 to gain more insight into how the firm should construct future campaigns.
\newline



\newpage
# References {-}
<div id="refs"></div>

\newpage
\renewcommand\thepage{A-\arabic{page}}
\setcounter{page}{1}

```{r, child='AppendixA.Rmd'}
```

\newpage
\renewcommand\thepage{B-\arabic{page}}
\setcounter{page}{1}

```{r, child='AppendixB.Rmd'}
```

\newpage
\renewcommand\thepage{C-\arabic{page}}
\setcounter{page}{1}

```{r, child='AppendixC.Rmd'}
```

\newpage
\renewcommand\thepage{D-\arabic{page}}
\setcounter{page}{1}

```{r, child='AppendixD.Rmd'}
```
