---
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
output: pdf_document
header-includes:
- \usepackage{setspace}
- \onehalfspacing
---

```{r setupD, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, highlight=FALSE, message=FALSE)
```

```{r}
# Library statements
```

# Appendix D: Comment incorporation {-}

Our team received a number of helpful comments regarding our first submission which helped us rein in the scope of our analytical project and decide what our focus was going to be. A number of factors led to us completely overhauling the concept for our project, which made the context of many of these comments obsolete. Nevertheless, we acknowledge the impact they made on the second version of our first deliverable here.
\newline

The Introduction section of our first deliverable described the context of our business problem and built up a narrative that incorporated the challenges retailers faced during the COVID-19 pandemic. At the time, we wanted to highlight the importance of maintaining customer loyalty amidst the crashing wave of digital commerce, and how these traditional retail businesses could benefit from adopting technology and data-driven strategies. One reviewer suggested that we include an in-depth explanation of CRM database systems in this section. Our team decided against this, in favor of keeping the section concise and proceeding under the assumption that our readers would already be familiar with this technology. Other comments suggested that we write less about the growing importance of technology and instead focus more on how brick-and-mortar retailers should be operating during the pandemic. This was a fair point, and we incorporated this feedback by removing some extra content on the growth of e-commerce and highlighting the struggles of traditional retailers. We also received quite a bit of positive feedback regarding the way we set up the background and context for our project, which was great to see.
\newline

The Business Problem section of our first deliverable began to introduce a few ways that traditional retailers would benefit from leveraging data analytics. These included the ability to deploy more effective online marketing campaigns by identifying key demographic groups and reflecting on past marketing efforts by analyzing key performance indicators. As mentioned earlier, we also wrote about the importance of building and maintaining customer loyalty during the pandemic times. We received a number of  comments here that alerted us to the fact that we weren’t conveying our business problem in a clear enough manner. We attempted to rectify this by restructuring the section and stating our business problem up front. However, it doesn’t seem as though we did a good enough job with the second version of this submission, as we received additional feedback regarding this same point. We hope that our goals come across more clearly now that we’ve made further adjustments to the section. Additionally, we received a lot of feedback regarding our decision to pursue solutions to the issue of customer loyalty maintenance. Our group agreed that this topic was slightly too vague, and that we would need to shift our focus to something else. This led us to commit to the aforementioned overhaul, which involved us focusing more on the performance of the firm that our dataset was based upon. Finally, we received a suggestion that said we should mention how e-commerce was becoming more common and accepted in the modern day. We decided that this would be unnecessary and redundant given that we provided similar context in the introduction section.
\newline

The Intended Audience section of our deliverable described the rapid growth of digital commerce across multiple industries during the COVID-19 pandemic, as well as the idea that traditional retailers had much to gain by building out an online platform. We received a few comments that raised concerns about the scope of our analysis. One acknowledged that our analysis would indeed benefit retail businesses across a wide variety of industries, and advised us to instead focus on just a few industries. The other suggested that we differentiate large brick-and-mortar retailers from smaller family-owned businesses. I believe that our team addressed both of these suggestions in our concept overhaul by choosing to focus on the firm our dataset was based upon. We received a comment regarding the verbosity of this section, and we incorporated the feedback by making efforts to shorten the section. The length of the final version of this section should reflect these changes. One comment suggested that we provide a citation to support one of the claims we made about how building an online presence could boost a retailer’s sales performance. This was information we gathered from a Deloitte report that was cited earlier in the document, so we inserted an extra citation here to make this clearer. Ultimately, however, this section was removed in order to tighten the focus of our final deliverable.
\newline

We also received general formatting feedback regarding the spacing between paragraphs and the content of our reference entries. We made sure to rectify the spacing issues in the later deliverables. Our team also updated the reference entries to accord with the new guidelines that were posted later into the semester.
\newline

We received quite a lot of good feedback on the Data section of the report which were relatively easy to incorporate. We responded to most of Professor Martinet’s comments by implementing a wide range of stylistic changes. Many of these changes involved replacing references to raw variable names with descriptive information regarding the content of the variables in question. We modified our figures by adjusting column labels where appropriate and appending captions where needed.
\newline

The Professor’s comments regarding our content allowed us to revise the section and make our writing more clear and cohesive. Most importantly, we were able to internalize some feedback and develop a clearer sense of direction regarding our analytic process. Additionally, this section of the report initially had a data dictionary that listed out each of our variables. We incorporated the Professor’s feedback here by reorganizing the variable descriptions into paragraph form.
\newline

We made changes to the data preparation details section by adding more text explanations to accompany our commented code chunks. We hope that the changes help future readers to better understand our data preparation process. Furthermore, we took some helpful advice here and moved some of our exploratory findings in Excel into the Descriptive Analytics section of the report.
\newline

Finally, we received a number of helpful comments from Professor Martinet regarding our in-text citations and the format of our bibliography. We were able to clarify some points of confusion and adjust the way we documented our sources both in the body of our text and in our references file. We also removed a number of unnecessary citations pertaining to the data manipulation steps we carried out in Excel and R.
\newline

We also received some feedback from the TA and our peers, which were slightly less helpful. For the data section, we were advised to explain how key variables like conversion, interest, and spent could be useful. This was valuable feedback and was easily incorporated into our deliverable, as we were able to simply just give a rationale for why we were interested in these variables. In addition, we were told that repeating the ad_id variable in the second row of kable output was useful. We eventually reorganized our kable output entirely, so this feedback didn’t end up being very useful.
\newline

For the data collection section, we primarily focused on adding more in-text citations into our deliverable to properly give credit for the information we were borrowing. We were also advised to consider adding some context by discussing data ethics or some background on Google Adwords. This ultimately led to us doing more background research on these topics and doing our best to incorporate them into the section. We discovered that the dataset actually pertained to Facebook ads, which was helpful for our later deliverables as well.
\newline

For the data preparation section, we were asked to consider transforming some of the values to be easier to interpret. We thought this made sense, as values that were easier to interpret would be more meaningful and useful. These were relatively simple changes to make in both R and Excel, and were documented in the relevant code walkthrough sections.
\newline

For the data preparation details in the R section, we were told that transforming the age to an integer was useful for analysis, but decreased the interpretability of the data, so we should leave it as is. We understood why the reviewer thought this was the case, but we ultimately decided against incorporating this feedback because we knew we would eventually transform this variable for our linear regression anyway.
\newline

For the data preparation details in Excel section,  we were told that the images were showing up in weird places and were too small. These were two things that were fairly simple to address in the R-markdown file with some changes to our R code that ultimately ended up in a more aesthetically pleasing output file.
\newline

For the Descriptive Analytics section, we incorporated Professor Martinet’s comment by changing some of the wording of the introduction. We definitely had lost sight of our audience and resorted to using statistical language throughout this section. Her comments helped make this section more understandable to a statistically illiterate reader. The TA’s comment mentioned that we forgot to include insights, but we had included these further down in the report. However, we realized that we didn’t provide any intermediate explanations after each figure. As such, we incorporated this feedback by including brief explanations after each graphic. Commenter 2 for this section was especially helpful as they suggested that we visualize gender and age disparities using a histogram. This made our visualizations more understandable to a non-statistician, as histograms are much more easily interpretable than box plots. Commenter 3 would have been helpful if we were writing this report for a statistical audience but since we explain the diagram further on in the report, we felt no need to get into the details of the transformation. Commenter 4’s comment about proportions were largely incoherent so we elected to ignore it.
\newline

Throughout this project it was easy to feel lost as none of us had a real business analytics background. Professor Martinet’s comment let us know we were on the right track and gave us the confidence to extend this type of analysis to further deliverables. We incorporated the TA’s comments by separating our insights by our variables rather than by our figures. This forced us to think about how the figures related to each other and our business problem. Wordiness and statistical language were definitely a problem throughout this report and we appreciated commenter 3’s suggestion. We changed the wording here to make the insights section more readable. We appreciated that commenter 4 could understand our insights even if others found them wordy. Their suggestion of comparing our rates to the general industry rates was especially helpful for garnering insights from the data, and we included this in our revised submission.
\newline

Professor Martinet’s comments suggested minor code changes that we incorporated in our revisions. The TA’s comments helped us a lot as we were previously unaware of the facet_wrap function. This improved our visualizations to make them slightly easier to interpret. Commenter 3 brought our attention to the fact that we were missing comments on our R code. We incorporated this feedback by adding more comments to our coding details section. We felt that this allowed the reader to follow our process with more ease. Commenter 4 made us realize that we were missing captions for certain plots. We quickly fixed this for our revised deliverable.
\newline

From all the feedback and comments on our deliverable 4 — both on the draft and on the final deliverable — we noticed a few consistent suggestions. At various points in our deliverable, our wording and explanations became a little too technical. For example, we used words such as RMSE, ANOVA, and so on. We replaced these words with phrases that were less technical, such as “prediction error” to replace RMSE. We also received a couple of comments regarding some confusing wording or redundant sentences in our deliverable. We attempted to go through our deliverables and edit phrases that were confusing to the readers. We also removed any redundant sentences we were able to find. Finally, there were some formatting issues throughout the deliverable in terms of how our tables and graphs were structured. Many of our tables used raw variable names such as “total_conv” that wouldn’t be very presentable to any executives reading our report. There were also some formatting issues in our analytics detail section which was easily fixable as well. For example, we were advised to add titles and axis labels for our residual plots and remove the captions of tables in our appendices.
\newline

Our draft for deliverable 4 contained repetitive information in the process and predictive analytics sections. We were advised to remove the repetitive information from one section, which we did. Additionally, our process section described the details of our linear regression and random forest methodologies rather than focusing on the actual process we followed to build our models. Similarly, we had described a lot of our modeling process in the assessments section, rather than the process section. We received various TA and Professor comments advising us to edit these sections. These comments were very helpful because they clarified the expectations regarding which content was to be included in each section. We edited our predictive analytics section to summarize our goals for our analysis, i.e. to determine what variables are significant to our two conversion rates. We then edited the process section to include a high level explanation of how we obtained our model. To ensure we did not make this section technical, we simply mentioned that we started off with a model with all of our variables and then created different models to compare after removing insignificant variables. A lot of this information was moved from our assessments section to our process section, as suggested.
\newline

In our assessments section, we were advised to remove the training set assessments as well as to move our testing set assessments from the results section to the assessments section. We removed the training set assessments because we realized that the assessment measures generated through this process were only used to gain information about how our model was being trained. However, they did not add to our analysis of finding the best model to conclude which variables are the most important predictors for our two conversion rates. We also removed the testing set assessment results from the results section and placed them within the assessments section. The comments helped us realize that it would be better for us to use the results section to discuss our final models and the variables contained therein. With this, the Professor suggested that we needed to make clear what exactly RMSE (prediction error) meant for our analysis since it did not actually give us information about how well our model predicts. We responded to this suggestion by explaining the importance of RMSE in a couple of sentences. In essence, we explained that we are interested in making inferences about the relationship between our two response variables and the selected predictors and that assessment measures like RMSE are relevant because they give us valuable information regarding the soundness of our models.
\newline

One peer also suggested we add information on linear regression assumptions through plots and graphs in our assessments section. We considered this, however, we thought it was too technical to add to this section and instead decided to elaborate on our assumptions check in the analytics detail section. Nevertheless, we did our best to keep our explanation of the regression assumptions as non-technical as possible. However, we did end up including a pair of scatter plots in the body of the report in order to demonstrate the linear relationships between our variables. We decided to only keep this in the section as the plot is easily digestible, even for someone who is not well versed in statistics. Initially, we included only a single plot showing all of the quantitative variables together. However, the Professor commented to make two separate graphs to make clear that the conversion rates were not being used in each others' models. We made the necessary changes as we realized that it would make our analysis more comprehensible as it reiterates that there are two separate response variables being analyzed. Additionally, separating it into two plots made the individual relationships between the variables more clear. 
\newline

Another comment spoke to the clarity of the random forest analysis, claiming that it was unclear whether the gender variable was important in our final model or if it was removed. We clarified this in the report by explaining that the gender and campaign dummy variables were removed for the pruned and reduced models because they had lower variable importance. However, our validation set model assessments indicated that the full models containing these variables had a better fit to our data. Thus, our final models do include the gender and campaign variables.
\newline

One peer suggested adding the summary outputs for the regression models as well as the variable importance table for our random forest analysis in the results section. This was a very useful suggestion that we immediately incorporated into our deliverable as these two outputs summarize what our model finally gives us and answers our question of what variables are the most important. 
\newline

Finally, we were advised by the Professor to rewrite the insights summary to explain the important variables separately instead of explaining the methods separately. This made a lot of sense to incorporate because a lot of the takeaways from both of the methodologies we employed were the same. By structuring this section around the variables rather than each method, we did not have to repeat the same takeaways multiple times. We also believe that these changes made our conclusions slightly easier to follow.
