---
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
output: pdf_document
bibliography: references.bib 
nocite: '@*'
header-includes:
- \usepackage{setspace}
- \onehalfspacing
---

```{r setup3, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, highlight=FALSE, message=FALSE)
```

```{r, warning=FALSE, echo=FALSE}
# Library Statements
library(tidyverse)
library(viridis)
library(gridExtra)
library(knitr)

# Initial Data Prep (covered in Deliverable 2)
mydata <- read_csv("~/RStudio/STAT 4220 - Biz Analytics/Data/conversion.csv")
mydata$fb_campaign_id <- NULL
mydata$interest <- NULL
names(mydata) <- tolower(names(mydata))
names(mydata)[names(mydata) == "gender"] <- "male"
names(mydata)[names(mydata) == "xyz_campaign_id"] <- "campaign"
names(mydata)[names(mydata) == "total_conversion"] <- "total_conv"
names(mydata)[names(mydata) == "approved_conversion"] <- "app_conv"
mydata$male[mydata$male == 'M'] <- 1
mydata$male[mydata$male == 'F'] <- 0
mydata$male <- as.integer(mydata$male)
mydata$age[mydata$age == '30-34'] <- 32
mydata$age[mydata$age == '35-39'] <- 37
mydata$age[mydata$age == '40-44'] <- 42
mydata$age[mydata$age == '45-49'] <- 47
mydata$age <- as.integer(mydata$age)
mydata$campaign[mydata$campaign == 916] <- "campaign_1"
mydata$campaign[mydata$campaign == 936] <- "campaign_2"
mydata$campaign[mydata$campaign == 1178] <- "campaign_3"
mydata$campaign <- as.factor(mydata$campaign)
```

# Descriptive analytics

The objective of this analytical project is to explore different KPIs and identify which ones contribute most strongly to the success of a marketing campaign. However, not all marketing campaigns are deployed in an identical manner, and it may not be appropriate to run a single model on data aggregated from all three of the campaigns if their characteristics are substantially different. We used a series of box plots to explore some quantitative characteristics associated with each marketing campaign in order to identify any potential differences therein.  We also transformed some of the variables for the sake of the visualizations. This was deemed worthwhile as the visualizations would otherwise have been heavily skewed due to some irregular data in Campaign 3.
\newline

Figure 1 below indicates that there appear to be substantial differences in the characteristics of each of the three campaigns. Campaign 3 appears to have consistently enjoyed the most user engagement in terms of clicks, impressions, and conversion, while also having the highest level of per-ad spending. This seems to set Campaign 3 apart from Campaigns 1 and 2, which seem more similar to each other in comparison.
\newpage

```{r, echo=FALSE, fig.height=4.5, fig.cap="Box Plots of Selected Campaign Characteristics"}
mydata$campaign <- recode(mydata$campaign,
                          "campaign_1" = "1",
                          "campaign_2" = "2",
                          "campaign_3" = "3")
p1 <- ggplot(mydata, aes(campaign, sqrt(clicks), fill=campaign)) + 
  geom_boxplot(outlier.shape=1, alpha=0.5) + 
  scale_fill_viridis(discrete="true", alpha=0.9) +
  labs(x="Campaign",
       y="Clicks",
       title="Clicks",
       subtitle="Square Root Transformation Applied") +
  theme(legend.position="none",
        plot.title=element_text(size=14),
        plot.subtitle=element_text(size=8)) +
  coord_flip()
p2 <- ggplot(mydata, aes(campaign, sqrt(impressions), fill=campaign)) + 
  geom_boxplot(outlier.shape=1, alpha=0.5) + 
  scale_fill_viridis(discrete="true", alpha=0.9) +
  labs(x="",
       y="Impressions",
       title="Impressions",
       subtitle="Square Root Transformation Applied") +
  theme(legend.position="none",
        plot.title=element_text(size=14),
        plot.subtitle=element_text(size=8)) +
  coord_flip()
p3 <- ggplot(mydata, aes(campaign, sqrt(spent), fill=campaign)) + 
  geom_boxplot(outlier.shape=1, alpha=0.5) + 
  scale_fill_viridis(discrete="true", alpha=0.9) +
  labs(x="Campaign",
       y="Spending",
       title="Per-Ad Spending",
       subtitle="Square Root Transformation Applied") +
  theme(legend.position="none",
        plot.title=element_text(size=14),
        plot.subtitle=element_text(size=8)) +
  coord_flip()
p4 <- ggplot(mydata, aes(campaign, sqrt(app_conv), fill=campaign)) + 
  geom_boxplot(outlier.shape=1, alpha=0.5) + 
  scale_fill_viridis(discrete="true", alpha=0.9) +
  labs(x="",
       y="Approved Conversion",
       title="Approved Conversion",
       subtitle="Square Root Transformation Applied") +
  theme(legend.position="none",
        plot.title=element_text(size=14),
        plot.subtitle=element_text(size=8)) +
  coord_flip()
mydata$campaign <- recode(mydata$campaign,
                          "1" = "campaign_1",
                          "2" = "campaign_2",
                          "3" = "campaign_3")
grid.arrange(p1,p2,p3,p4, ncol=2)
```

In addition to the boxplots above, a table detailing the number of advertisements per marketing campaign is included below to further highlight a potential difference between the three marketing campaigns.

```{r, echo=FALSE}
mydata$campaign <- recode(mydata$campaign,
                          "campaign_1" = "1",
                          "campaign_2" = "2",
                          "campaign_3" = "3")
mydata %>%
  count(campaign) %>%
  kable(col.names = c("Campaign","Count"),
        caption="Advertisement Counts Per Campaign")
mydata$campaign <- recode(mydata$campaign,
                          "1" = "campaign_1",
                          "2" = "campaign_2",
                          "3" = "campaign_3")
```

Table 1 indicates a substantial disparity in advertisement count between the three marketing campaigns. Campaigns 2 and 3 have counts in the hundreds, whereas there are only 54 advertisements in Campaign 1. We will need to keep this in consideration when interpreting our results, as this disparity may introduce undesirable bias and variability.
\newline

Next, we used a scatter plot of the various quantitative variables in our data to explore the relationships between the variables. Here, the variables are not differentiated by campaign as we wanted to explore the overarching interactions between the different KPIs, which will aid us in later analyses.
\newline

Figure 2, displayed below, indicates a positive relationship between all of our quantitative variables. The strongest relationships appear to be between the amount paid to have a particular advertisement delivered and the number of clicks and impressions generated by the particular advertisement. The weakest relationship seems to be between the number of times a user within a particular audience clicked on a particular ad and the resulting number of conversions, or users who ultimately bought the product after seeing the ad.

```{r, echo=FALSE, fig.cap="Correlation Plots of Quantitative Predictors"}
pairs(mydata[5:9], 
      labels = c("Impressions","Clicks","Spending",
                 "Total Conversion","Approved Conversion"),
      lower.panel = NULL)
```

In addition to the scatter plots above, a correlation matrix is included below to augment our exploration of the quantitative variables.

```{r, echo=FALSE}
correlation = as.data.frame(row = c("Impressions","Clicks","Spending",
                                    "Total Conversion","Approved Conversion"),
                            round(cor(mydata[5:9]), 3))
names(correlation) <- c("Impressions","Clicks","Spending",
                        "Total Conversion","Approved Conversion")
kable(correlation, 
      caption="Correlation Matrix of Quantitative Predictors")
```

Table 2 provides a matrix of correlation coefficients associated with the variable relationships depicted in the preceding scatter plots. This allows us to more confidently compare the relative strengths and weaknesses of the variable relationships. For instance, we can now assert that the strongest positive correlation between our quantitative variables can be found between per-ad spending and the number of user clicks generated by a particular advertisement.
\newline

Lastly, we used a series of bar plots to explore the demographic distribution of the various audiences the ads were presented to. Figure 3 indicates that the 30-34 age bracket occurs most frequently across all audiences, which suggests that it may be the firm’s primary target demographic. At a total of 426 instances, this demographic occurs almost twice as often as any of the other age groups. The 45-49 age bracket comes second, with a total of 259 instances. It is also worth noting that the firm tends to target more male audiences than female audiences.
\newpage

```{r, echo=FALSE, fig.cap = "Bar Plots of Age and Gender Distributions"}
mydata$male <- recode(mydata$male, 
                      "0"="Female", 
                      "1"="Male")
mydata$age <- recode(mydata$age,
                     "32" = "30-34",
                     "37" = "35-39",
                     "42" = "40-44",
                     "47" = "45-49")
ggplot(mydata, aes(x=age, fill=as.factor(age))) + 
  geom_bar(show.legend = FALSE) +
  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +
  facet_wrap(~male) +
  scale_fill_viridis(discrete="true", alpha=0.9) +
  labs(x = "Age Brackets",
       y = "Count",
       title = "Distribution of Audiences by Age and Gender") +
  lims(y=c(0,250))
mydata$male <- recode(mydata$male, 
                      "Female" = 0, 
                      "Male" = 1)
mydata$age <- recode(mydata$age,
                     "30-34" = 32,
                     "35-39" = 37,
                     "40-44" = 42,
                     "45-49" = 47)
```



## Insight summary

As previously stated, Figure 1 and Table 1 indicate that the characteristics of the three campaigns appear to be substantially different. Campaign 3 demonstrates the highest median value and variability across most of the selected quantitative performance metrics. It also appears as though the firm invested the most money into Campaign 3 given that the deployed advertisements tended to have higher levels of per-ad spending. As a result, Campaign 3 seems to have achieved a higher level of user engagement, though it would be too early to draw any causal conclusions at this point. It is worth noting that there is a large degree of disparity between the number of advertisements deployed within each campaign. As previously mentioned, this may have interesting statistical implications for our predictive results going forward.
\newline

Figure 2 and Table 2 show positive relationships between each of the quantitative variables within this data set. The very strongest positive relationship is found between the amount spent on a particular advertisement and the number of clicks generated, with a correlation coefficient of 0.993. The next strongest positive relationship can be found between the amount spent on a particular ad and the number of impressions generated, with a correlation coefficient of 0.970. These findings appear to accord with Facebook’s cost per link click (CPC) pricing model, whereby advertisers are charged solely based on the number of times their ad was clicked on (WebFX 2021). Additionally, a further inspection of our data showed that there were no advertisements with zero clicks generated for which spending was nonzero. This supports the theory that the firm chose to pursue a CPC pricing model because it suggests the firm did not pay for advertisements that did not generate any clicks. As such, it would make sense that the highest correlation coefficient is associated with the relationship between per-ad spending and number of clicks generated.
\newline

This investigation is relevant because there are a wide variety of pricing models that Facebook offers to advertisers. One alternative pricing model is based on cost per thousand impressions (CPM), whereby advertisers are instead charged based on the number of times their advertisement is shown on a user’s screen (Facebook 2020). However, we know now that the firm did not elect to choose a CPM pricing model, which indicates that the relatively high correlation coefficient between per-ad spending and impressions is not directly related to the firm’s marketing campaign design. Rather, it may simply be the case that increasing spending on an advertisement with the goal to generate more clicks also increases its visibility to users, which might intuitively lead to a greater number of impressions. Since our team is interested in uncovering less intuitive insights from our firm’s data, it may be beneficial to control for per-ad spending in further analyses. This might allow us to identify other variables that might lead to higher values of impressions, clicks, and other KPI’s.
\newline

On the other hand, the weakest positive relationship is noted between the number of times a user within a particular audience clicked on a particular ad and the number of resultant conversions. This finding seems to be consistent with landing page conversion rates across a majority of industries. Studies have found that these conversion rates tend to be quite low, ranging from 2.6% to 6.1% (Unbounce n.d.). As such, we might expect a relatively weaker link between advertisement clicks and conversions towards actual sales.
\newline

The distributions depicted in Figure 3 provide a few interesting insights into what the firm’s preferred target demographics may be. When gender is factored in, the most frequently occurring demographic is associated with audiences consisting of males aged 30 to 34. Audiences consisting of females aged 30 to 34 come at a close second. The three remaining age demographics occur with relatively similar frequency, with roughly 200 to 250 audiences associated with each. It may prove interesting to investigate the effectiveness of the firm’s supposed targeting strategy. This could conceivably be accomplished by comparing the level of spending devoted to each demographic group as well as their respective conversion rates.